---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# histgadm

[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/8a3jtxe4uiehushs/branch/master?svg=true)](https://ci.appveyor.com/project/epixproject/histgadm-cs9wa/branch/master)
[![Travis build status](https://travis-ci.org/epix-project/histgadm.svg?branch=master)](https://travis-ci.org/epix-project/histgadm)
[![Coverage status](https://codecov.io/gh/epix-project/histgadm/branch/master/graph/badge.svg)](https://codecov.io/github/epix-project/histgadm?branch=master)
[![CRAN status](https://www.r-pkg.org/badges/version/histgadm)](https://cran.r-project.org/package=histgadm)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)

`histgadm` is a workflow package: From current map from GADM (https://gadm.org/) recreates historical administrative boundaries map and creates one or multiple packages (one by country inputed) containing the data and the documentation.

## Installation

You can install the development version of histgadm from [GitHub](https://github.com/epix-project/histgadm) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("epix-project/histgadm")
```

## Usage

The `histgadm` contains four functions. 

The function `init_package` creates a package for the GADM data (https://gadm.org/), and interactively allows the user to download data from GADM for one or more country and recreates historical map from a time range (interactive input) by merging or spliting back admin1 polygons. The ouput are `sf` maps of the country in high and low definition with the different admin1 historial and current administrative boundaries but also the country administrative boundaries. The historical map are "approximate" map because the package only split or merge admin1 polygons when in reality, this event are ofter more complexe and the boundaries may not be exact. 

Below is a quick look at how `histgadm` is working:
```{r}
library("histgadm")

# Create a new package ---------------------------------------------------------
tmp <- file.path(tempdir(), "pkgtest")
dir.create(tmp)
initial_pkg(tmp, "test")
```

By default, the package created contained no data but if `y` is answer the package will then ask the user to imput at least one country name and a time range to download the data corresponding to gadm and to recreate the historical map corresonding to the time range inputed.
Currently, it works only for `Cambodia, Laos, Thailand and Vietnam`. 

For other country, the users will need to use the functions `map_data`, `map_documentation` to complete their packages. For more details, please take a look at the vignettes `histgadm Usage`.
