---
title: "histgadm Usage"
author: "Contamin Lucie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
knit: (function(inputFile, encoding, output_dir) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_dir=paste0(dirname(normalizePath(getwd())), "/inst/doc"))})
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r include = FALSE}
knitr::knit_hooks$set(margin = function(before, options, envir) {
  if (before) par(mgp = c(1.5, .5, 0), bty = "n", plt = c(0, 1, 0, 1))
  else NULL
})

knitr::opts_chunk$set(margin = TRUE, prompt = TRUE, comment = "",
                      collapse = TRUE, cache = FALSE,
                      dev.args = list(pointsize = 11), fig.height = 3.5,
                      fig.width = 4.24725, fig.retina = 2, fig.align = "center")
```

## Installation

You can install the development version of histgadm from [GitHub](https://github.com/epix-project/histgadm) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("epix-project/histgadm")
```

## Usage

The `histgadm` contains four functions that works together. The function `hist_map` creates historical map, the functions `map_data` & `map_documentation` call the function `hist_map` in the environment of a package and stock the results (maps in `.rda` files and documentation) and download file in the folder corresponding. The function `init_package` called the three functions to create interactively with the user a package containing data, source files and documentation. 
```{r}
library(histgadm)
```

### `hist_map`

The function `hist_map` creates `sf` objects of historical admin1 administrative boundaries by merging back together, renaming or splitting admin1 polygons from the current admin1 administrative boundaries downloaded from GADM https://gadm.org for one country, one time range and by a list of events provided by the user. 

For example, for Vietnam: the user will need to input a list containing the historical event and a dictionary for the admin1, admin2 names (if necessary) .
For that, the package `dictionary` can be used as it contains functions to create them but also dictionary and list of event for Cambodia, Laos, Thailand and Vietnam.
To install it:
``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("choisy/dictionary")
```

Let's take a look at it: 
```{r}
library(dictionary)
head(vn_admin1) # dictionary for the admin1 names
tail(vn_admin1)
head(vn_history, 1) # list of event in admin1 history in vietnam
```

Now, we can use the function `hist_map` to create "historical" map of Vietnam in between 2000 and 2019:
```{r}
a <- hist_map("Vietnam", vn_admin1, vn_history, from = 1980, to = 2019)
```

We can look in more details at the results
```{r}
length(a)
```

and look at the first and last element:
```{r}
head(a, 1)
tail(a, 1)
```

We can plot the first and last maps of the list to be able to see the difference:
```{r}
library(sf)
plot(st_geometry(a$vn_1980_1990))
plot(st_geometry(a$vn_2008_2020))
```

The output of the function is a named list containing, for each time step from the most recent to the oldest, one map of admin1 administrative boundaries. Each object in the list is named by the 2 characters ISO code of the country corresponding (by using the package countrycode), the year of expression of these admin1 administrative boundaries and the resolution. 
For example, here we have:
```{r}
names(a)
```
`vn_2000_2004` for the admin1 boundaries of Vietnam from 2000-01-01 until 2004-01-01 (not include). 

Be careful, the historical map are "approximate" map because the package only split or merge back together admin1 polygons when in reality, this event are often more complex.

### `map_data` & `map_documentation`

The users can also use the functions `map_data`, `map_documentation` to complete their packages. 
Let's now take a look at `map_data`: it download the current map from GADM and recreates historical map:
```{r}
tmp <- file.path(tempdir(), "pkgtest")
usethis::create_package(tmp, open = FALSE)
histgadm::map_data(tmp, "Cambodia", dictionary::kh_admin1, dictionary::kh_history, from = "1980", to = "2018")
```
The arguments `save` permits to store the source file from gadm in a folder `\data-raw` in the package inputted.

If we look at the folder in the packages:
```{r}
dir(paste0(tmp, "/data"))
dir(paste0(tmp, "/data-raw"))
```

We can see that object were downloaded and created in the package, corresponding to the historical map in `sf` object saved in `.rda` format in `data` folder and source files saved in `raw-data`. 

And the function `map_documentation` will create the documentation for each object by creating a file `data.R` written in roxygen and a also by creating `.rd` file(s) in the folder `man` of the package.
```{r}
map_documentation(tmp)
```

If we look at the folder in the packages:
```{r}
dir(paste0(tmp, "/R"))
dir(paste0(tmp, "/man"))
```

We can see that documentation corresponding to the object in the package were created: a `.R` file with roxygen comment who was roxigenize to make the files in the `man` folder.

### `init_package`

The function `init_package` creates a package for the GADM data (https://gadm.org/), and interactively allows the user to download data from GADM for one or more country and recreates historical map from a time range (interactive input) by merging or spliting back admin1 polygons. The ouput are `sf` maps of the country with the different admin1 historial and current administrative boundaries.

Below is a quick look at how `histgadm` is working:
```{r, eval = FALSE}
# Create a new package ---------------------------------------------------------
tmp <- file.path(tempdir(), "pkgtest")
dir.create(tmp)
initial_pkg(tmp, "test")
```

By default, the package created contained no data but ask the user to imput at least one country name and a time range to download the data corresponding to and to recreate the historical map corresonding to the time range inputed.
Currently, it works only for `Cambodia, Laos, Thailand and Vietnam`. 
