---
title: "histgadm Usage"
author: "Contamin Lucie"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Installation

You can install the development version of histgadm from [GitHub](https://github.com/epix-project/histgadm) with:

``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("epix-project/histgadm")
```

## Usage

The `histgadm` contains four functions. 

The function `init_package` creates a package for the GADM data (https://gadm.org/), and interactively allows the user to download data from GADM for one or more country and recreates historical map from a time range (interactive input) by merging or spliting back admin1 polygons. The ouput are `sf` maps of the country in high and low definition with the different admin1 historial and current administrative boundaries but also the country administrative boundaries. The historical map are "approximate" map because the package only split or merge admin1 polygons when in reality, this event are ofter more complexe and the boundaries may not be exact. 

Below is a quick look at how `histgadm` is working:
```{r}
library("histgadm")

# Create a new package ---------------------------------------------------------
tmp <- file.path(tempdir(), "pkgtest")
dir.create(tmp)
initial_pkg(tmp, "test")
```

By default, the package created contained no data but if `y` is answer the package will then ask the user to imput at least one country name and a time range to download the data corresponding to gadm and to recreate the historical map corresonding to the time range inputed.
Currently, it works only for `Cambodia, Laos, Thailand and Vietnam`. 

## For other country

For other country, the users will need to use the functions `map_data`, `map_documentation` to complete their packages. 
If the user want to recreate historical map, it will need to input a list containing the historical event and a dictionary for the admin1, admin2 names. 
For now, the package `dictionary` contains functions to create them but also dictionary and list of event for Cambodia, Laos, Thailand and Vietnam.

To install it:
``` {r, eval = FALSE}
# install.packages("devtools")
devtools::install_github("choisy/dictionary")
```

Let's now take a look at `map_data`: it download the current map from GADM and recreates historical map:
```{r}
pgkg_dir <- paste0(tmp, "/test")
map_data(pgkg_dir, "Cambodia", dictionary::kh_province, dictionary::kh_history, from = "1980", to = "2018")
```

And the function `map_documentation` will create the documentation for each object.
```{r}
map_documentation(pgkg_dir)
```

